Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-13 paper.tex
Wrote a skeleton

\section{The Rips complex and the Gromov boundary}\label{sec:approximating}

@@

\section{Connectivity and double dagger conditions}\label{sec:connectivity}

\subsection{Connectivity conditions}

Recall the following standard definitions of topological connectedness 
properties.

\begin{definition}
  The space $M$ is \emph{$d$-locally-connected} (abbreviated $\LC{d}$) if for any 
  point $p \in M$ and any neighbourhood $U$ of $p$, $U$ contains a 
  subneighbourhood $V$ of $p$ such that any continuous map $S^i \to V$ for $i 
  \leq d$ is homotopic in $U$ to a constant map.

  A topological space $M$ is \emph{$d$-connected} (abbreviated $\C{d}$) if 
  any continuous map $S^i \to M$ for $i \leq d$ is homotopic to a constant map.
\end{definition}

We also define a quantitative version of the condition $\LC{d}$.

\begin{definition}
  A metric space $M$ is \emph{linearly-$d$-locally-connected} (abbreviated 
  $\lLC{d}$) if there exists constants $\lambda$ and $r_0$ such that for any 
  point $p \in M$ and any number $r \in (0,r_0)$, any continuous map $S^i \to 
  \Ball_p(r)$ for $i \leq d$ is homotopic in $\Ball_p(\lambda r)$ to a constant 
  map.
\end{definition}

\subsection{Combinatorial conditions}

In \cref{sec:criterion,sec:dd,sec:assembling} we relate local connectivity
properties, applied to the boundary of a hyperbolic group, to certain
combinatorial properties of spheres in the Rips complex of the group. We now
define these conditions. Let $G$ be a hyperbolic group and let $K_n$ be the
simplicial complex defined in \cref{sec:approximating}.

\begin{definition}
  Let $J$ be a simplicial complex. Let $\gamma \from J \to \boundary G$ be 
  continuous and let $f\from J \to K_n$ be affine. We call the triple $(J, 
  \gamma, f)_n$ a \emph{factored triple} or a \emph{factoring of $f$} if $f$ is 
  affine homotopic to $p^\infty_n\composed\gamma$. In this case we say that $f$ 
  \emph{admits a factoring}.
\end{definition}

\begin{definition}
  Let $d\geq -1$. We say that $X$ satisfies $\dd{d}$ if, for any $k$, there
  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
  then further assume that the diameter of the image of $f$ is at most $k$.
  Then $f$ admits an affine extension to $\sd^{k'}\Delta^{d+1}$.
\end{definition}

We also introduce the following a priori stronger condition.

\begin{definition}
  Let $d\geq -1$. We say that $X$ satisfies $\Sd{d}$ if, for any $k$, there
  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
  then further assume that the diameter of the image of $f$ is at most $k$.
  Then $\gamma$ admits a continuous extension $\gamma'$ to $\Delta^{d+1}$ and
  $f$ admits an affine extension $f'$ to $\sd^{k'}\Delta^{d+1}$ such that
  $(\sd^{k'}\Delta^{d+1}, \gamma', f')$ is a factored triple.
\end{definition}

\begin{remark}
  The base cases $\dd{-1}$ and $\Sd{-1}$ are each equivalent to the statement
  that $G$ is infinite.
\end{remark}

\begin{remark}
  The condition $\dd{0}$ is related to the double dagger condition of 
  Bestvina and Mess~\cite{bestvinamess91}. This is the reason for the choice 
  of notation.
\end{remark}

\subsection{Extending maps between simplicial complexes}

The conditions $\dd{-1}$ and $\Sd{-1}$ allow us to extend certain maps from
subcomplexes of simplicial complexes into $K_n$ in a controlled way. We now
prove a lemma to this effect.

\begin{lemma}\label{lem:extendingaffinemaps1}
  Suppose that $G$ satisfies $\Sd{d}$. Let $k \geq 0$. Then there exist numbers
  $k'$ and $n_0$ with the following property. Let $n \geq n_0$, let $J$ be a
  simplicial complex, let $J'$ be a subcomplex of $J$ containing all vertices
  of $J$ and all simplices of $J$ with dimension greater than $d+1$ and let $f$
  be a map $J' \to K_n$ satisfying the following conditions.
  \begin{enumerate}
    \item The map $f$ admits a factoring.
    \item The map $f$ is affine on the subdivision $\sd^k J'$.
    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
      $\dist(f(x), f(y)) \leq k$.
  \end{enumerate}
  Then $f$ admits an extension to $J$ that is affine on the subdivision
  $\sd^{k'} J$ and that admits a factoring.
\end{lemma}

\begin{proof}
  We prove the statement by induction on the maximal dimension of a simplex of
  $J$ that is not contained in $J'$. Let this dimension be $d'$, so $1 \leq d'
  \leq d+1$.

  By the inductive hypothesis there exist $k'$ and $n_0$ such that if $n \geq
  n_0$ and $f\from J' \to K_n$ is a map satisfying the conditions of the lemma
  then $f$ admits an extension $f'$ to $J' \union \Skel^{d'-1} J$ such that $f'$
  admits a factoring and is affine on the subdivision $\sd^{k'} (J' \union
  \Skel^{d'-1} J)$.

  The condition $\Sd{d}$ tells us that there exists $n_0' \geq n_0$ and $k''$
  such that for all $n \geq n_0'$ and any affine map $g \from
  \sd^{k'}\boundary\Delta^{d'}\to K_n$ that admits a factoring, $g$ admits an
  affine extension to $\sd^{k''}\Delta^{d+1}$ that extends the factoring.
  For each $d$-simplex $\sigma$ of $J$ not contained in $J'$, apply this fact
  to the map $f'\restricted{\boundary\sigma}$ to extend $f'$ to a map $f''\from
  J\to K_n$ that admits a factoring and is affine on $\sd^{k''} J$.
\end{proof}

If we weaken the conclusion of \cref{lem:extendingaffinemaps1} by no
longer insisting that the extension admit a factoring, then we can weaken the
assumptions to obtain the following proposition.

\begin{proposition}\label{prop:extendingaffinemaps2}
  Suppose that $G$ satisfies $\Sd{d-1}$ and $\dd{d}$. Let $k \geq 0$. Then
  there exist numbers $k'$ and $n_0$ with the following property. Let $n \geq
  n_0$, let $J$ be a simplicial complex, let $J'$ be a subcomplex of $J$
  containing all vertices of $J$ and all simplices of $J$ with dimension
  greater than $d+1$ and let $f$ be a map $J' \to K_n$ satisfying the following
  conditions.
  \begin{enumerate}
    \item The map $f$ admits a factoring.
    \item The map $f$ is affine on the subdivision $\sd^k J'$.
    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
      $\dist(f(x), f(y)) \leq k$.
  \end{enumerate}
  Then $f$ admits an extension to $J$ that is affine on the subdivision
  $\sd^{k'} J$. Furthermore $f\restricted{J' \union \Skel{d} J}$ admits a
  factoring.
\end{proposition}

\begin{proof}
  Apply \cref{lem:extendingaffinemaps1} until the final inductive step, which
  can be proved exactly analogously to the proof of the inductive step in
  \cref{lem:extendingaffinemaps1}.
\end{proof}

\section{A criterion for $d$-local-connectedness}\label{sec:criterion}

The goal in this section is to prove the following theorem.

\begin{restatable}{theorem}{ddagimpliesLCd}
  \label{thm:ddagimpliesLCd}
  Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and $\dd{d}$. Then 
  $\boundary G$ is $\lLC{d}$.
\end{restatable}

\subsection{Constructing maps to $\boundary G$}

We will make frequent use of the following lemma, adapted 
from~\cite{bestvinamess91}

\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.

  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
\end{lemma}

\begin{proof}
  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
  follows from another application of the triangle inequality.
\end{proof}

We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
proposition.

\begin{proposition}\label{prop:ddag_implies_i}
  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
  K_{n+1}$ such that the following conditions hold.
  \begin{enumerate}
    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
      \epsilon$.
    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
      K_n$ of $\Skel_{d+1}K_n$.
    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
  \end{enumerate}
\end{proposition}

\begin{proof}
  The condition $\dd{-1}$ implies the infinitude of $G$, so
  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.

  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
  factoring.

  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
  properties.
\end{proof}

Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
$\Skel_{d+1} K_m$.

In what follows we require the following useful lemma.

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{align*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{align*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

\begin{proof}
  We estimate the Gromov product using the visual metric $\vdistance$ on 
  $\boundary G$; then the claimed inequality follows from the triangle 
  inequality.

  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
  8\delta)/2$.

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{align*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{align*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{align*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{align*}

  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{align*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
  \end{align*}
  as required.
\end{proof}

\begin{lemma}\label{lem:linearproduct}
  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{x} \geq m - C
  \end{align*}
  for all $n\geq m\geq n_0$.
\end{lemma}

\begin{proof}
  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
  = \dist(e, y_n)$.

  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
  \leq RD$.  Putting this together,
  \begin{align*}
      \dist(y_n, y_{n+1}) \leq \epsilon + RD
  \end{align*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.

  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
  that
  \begin{align*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{align*}
\end{proof}

\begin{corollary}
  For $m \geq n_0$ and $x \in \Skel_{d+1} K_m$, the sequence
  $(i^m_n(x))_{n\geq m}$ converges to a point in $\boundary G$, which we shall
  denote $i^m_\infty(x)$.
\end{corollary}

\begin{proof}
  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
  tends to infinity as $n_1$ and $n_2$ tend to infinity.
\end{proof}

\begin{lemma}\label{lem:simplexproduct}
  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
  common simplex of $\Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
  \end{align*}
  for all $n\geq m$.
\end{lemma}

\begin{proof}
  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
  and $y$. By~\cite{bridsonhaefliger99} there exist $\delta'$ depending only on 
  $\delta$ such that
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
    &\geq m - C'
  \end{align*}
  for some constant $C'$.
\end{proof}

The following corollary immediately follows from \cref{lem:simplexproduct}.

\begin{corollary}\label{cor:visualdiameter}
  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
  $\sigma$ of $\Skel_{d+1} K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
  where $a$ is the visual parameter.
\end{corollary}

\begin{proposition}\label{prop:continuouslimit}
  The map $i^m_\infty\from \Skel_{d+1} K_m \to \boundary G$ is continuous.
\end{proposition}

\begin{proof}
  Fix $x \in \Skel_{d+1} K_m$. Let $k$ be the constant given in the definition 
  of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
  \Skel_{d+1}K_m$ of the minimal simplex of $\beta^{nk}\Skel_{d+1}K_m$ 
  containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.

  For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
  $\beta^{nk}\Skel_{d+1}K_m$ is affine, and therefore has image contained in a 
  simplex of $\Skel_{d+1} K_{m+n}$. The point $x$ is contained in every simplex 
  of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
  are contained in a common simplex of $\Skel_{d+1}K_m$. Therefore, by 
  \cref{cor:visualdiameter}, there is a constant $C$ such that 
  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $y \in 
  U_n$.
\end{proof}

\begin{remark}
  In fact, if $K_m$ is endowed with a metric in which each simplex is 
  isometrically identified with the standard simplex of the same dimension then 
  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
  only depending on $\delta$ and the constants in the definition of the map $i$. 
  We do not require this strengthening of \cref{prop:continuouslimit} 
  here.
\end{remark}

Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
special maps to $\boundary G$.

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
  \begin{enumerate}
    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
      $\boundary\Delta^{d+1}$;
    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
      $\newdist(f_0(x), f_1(x))$ is at most $C$;
    \item each of $f_0$ and $f_1$ admits a factoring.
  \end{enumerate}
  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
  \end{align*}
\end{proposition}

\begin{proof}
  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
  proposition holds.

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{align*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{align*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

  Let $\eta_0$ be such that for $\eta$ at most $\eta_0$, 
  for any $x \in \Delta^d$, for any $s$ and $t$ in $[0,1]$ with
  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
  union of at most two $(d+1)$-simplices of $\sd^{k'}(\Delta^d \times [0,1])$.
  We first define the modulus of continuity $\mu(\eta)$ for $\eta > \eta_0$.

  Let $M$ be the number of $(d+1)$-simplices in $\sd^{k'}(\Delta^d \times
  [0,1])$.  \Cref{cor:visualdiameter} gives a constant $C_0$ such that any
  $(d+1)$-simplex of $K_n$ is mapped to a subset of $\boundary G$ of diameter
  at most $C_0 a^{-n}$, and so we can take $\mu(\eta) = C_0M$ for $\eta >
  \eta_0$.

  Now, for $\eta \leq \eta_0$, there exists a maximal number $\kappa(\eta) \geq
  0$ such that for any $x \in \Delta^d$ and any $s$ and $t$ in $[0,1]$ with
  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
  union of at most two $(d+1)$-simplices of
  $\sd^{\kappa(\eta)}\sd^{k'}(\Delta^d\times[0,1])$. Note that $\kappa(\eta)
  \to \infty$ as $\eta \to 0$. Now, if $N\in\naturals$ then a $(d+1)$-simplex of
  $\sd^{k^N}K_n$ is mapped by $i^n_{n+N}$ into a $(d+1)$-simplex of $K_{n+N}$,
  which is mapped by $i^{n+N}_\infty$ to a set of diameter at most
  $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
  for $x \in \boundary\Delta^{d+1}$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
  h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
  \begin{align*}
    \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
  \end{align*}
\end{proof}

\subsection{Proving \Cref{thm:ddagimpliesLCd}}

We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
with two lemmas.

\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
  $Ca^{-m}$ for each $m$, where $a$ is the visual parameter.
\end{lemma}

\begin{proof}
  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
  constant $C$ such that 
  \begin{align*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{align*} 
  for each $n\geq m\geq n_0$.

  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_{d+1}K_m$ containing 
  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
  that
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
            - 2\delta' \\
          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
          &\geq m - C'
  \end{align*}
  for some constant $C'$.

  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
  from which the claim follows.
\end{proof}

\begin{lemma}\label{lem:name_this}
  There is a number $C$ such that, for any $\xi \in \boundary G$ and any $n
  \geq 0$ and any vertices $x_1$ and $x_2$ of the minimal simplices containing
  $i^n_{n+1}\composed p^\infty_n(\xi)$ and $p^\infty_{n+1}(\xi)$ respectively,
  \begin{align*}
    \dist(x_1, x_2) \leq C.
  \end{align*}
\end{lemma}

\begin{proof}
  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
  is bounded by $D$.

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
  2D$.
\end{proof}

\begin{proposition}\label{prop:uniform_homotopies}
  There exists a number $m_0$ and a function $\nu\from\posreals\to\posreals$ such
  that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
  $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be a continuous map. Let $n
  \geq m_0$ and let $f$ be an affine approximation to
  $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^{d+1}$ and
  any $s$ and $t$ in $[0,1]$,
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
  \end{align*}
\end{proposition}

\begin{proof}
  Let $C$ be as in \cref{lem:name_this} and apply \cref{prop:basic_homotopies}
  to obtain a number $m_0\geq n_0$ and a function $\mu$.

  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$, $n\geq m_0$ and
  $f\from\boundary\Delta^{d+1}\to K_n$ be as in the proposition. Let $f_0 = f$,
  and for $m > 0$ let $f_m\from\boundary\Delta^{d+1}\to K_{n+m}$ be a
  simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
  let $\gamma_m = i^{m+n}_\infty\composed f_m$. For each $m\geq 0$ the
  following observations are immediate:
  \begin{enumerate}
    \item the map $f_m$ admits a factoring;
    \item the image of $f_m$ is contained in the $d$-skeleton of $K_{n+m}$, and
      so $i^{n+m}_{n+m+1}\composed f_m$ admits a factoring;
    \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^{d+1}$.
  \end{enumerate}
  Therefore, for each $m$, \cref{prop:basic_homotopies} gives a homotopy $h_m$
  from $i^{n+m+1}_\infty\composed f_{m+1}$ to $i^{n+m}_\infty \composed f_m$
  satisfying a uniform continuity condition. Define an infinite concatenation
  of these homotopies:
  \begin{align*}
    h(x,t) = 
    \begin{cases}
      \gamma(x) & \text{if } t = 0\\
      h_n\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
              & \text{if $t \in \left[\frac{1}{2^{m+1}}, \frac{1}{2^m}\right]$
                    , $m\geq 0$}.
    \end{cases}
  \end{align*}
  This function is clearly continuous except possibly on
  $\boundary\Delta^{d+1}\times\{0\}$. We aim to show it is also continuous
  there, but first we define the function $\nu$.

  Let $m \in \naturals$. We aim to bound the distance $\rho(h(x,s), h(x,t))$
  for $\abs{s,t} \leq 2^{-m}$ independently of $n$ and the particular path
  $\gamma$. We first treat the case when one of $s$ and $t$ is $0$, then we
  deal with the case when $s$ and $t$ are small, and finally we treat the case
  when $s$ and $t$ are large. (Our ``small'' and ``large'' regions intersect,
  to guarantee that this covers all possibilities.)

  To begin, we bound the distance $\rho(h(x,0), h(x,t))$
  where $x \in \boundary \Delta^{d+1}$ and $t < 2^{-m}$. Let $C'$ be the
  constant appearing in \cref{lem:convergestoidentity}. Then 
  \begin{align*}
    \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
  \end{align*}
  Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
  \begin{align*}
    \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
  \end{align*}
  It follows that for $t \leq 2^{-m}$,
  \begin{align*}
    \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
          \mu(1)a^{-m'}\right).
  \end{align*}

  Similarly, we treat the ``small'' case. Here $s$ and $t$ are \emph{small} if
  they are at most $2^{-m/2}$. If $s$ and $t$ are both at most this large
  then
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
  \end{align*}

  Finally, if $s$ and $t$ are such that $\abs{s-t} \leq 2^{-m}$ but at least
  one of $s$ and $t$ is greater than $2^{-m/2}$ then both $s$ and $t$ are at
  least $2^{-m/2}$. This is the ``large'' case. It follows that 
  \begin{align*}
    \rho(h(x,s), h(x,t)) &\leq a^{-n} \mu(\abs{s-t} 2^{m/2 + 1}) \\
                         &\leq a^{-n} \mu(2^{1-m/2})
  \end{align*}

  Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
  \begin{align*}
    \nu(\eta)  = \max\left\{
      C'a^{-m} + \sum_{m' \geq m} \mu(1)a^{-m'},
      \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'},
      \mu(2^{1-m/2})
    \right\},
  \end{align*}
  and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
  \end{align*}
  for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.

  It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
  $\boundary\Delta^{d+1}$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
  $x$ in $\boundary\Delta^{d+1}$ such that $\rho(\gamma(x), \gamma(y)) \leq
  \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
  \epsilon/2$. Then for any $(y, t) \in U \times [0, \eta]$, $\rho(h(x,0),
  h(y,t)) < \epsilon$.
\end{proof}

\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.

\ddagimpliesLCd*

>>>>

\section{The Rips complex and the Gromov boundary}\label{sec:spheres}

@@

\section{Horoballs in the Rips Complex}

\section{The double dagger condition}

We begin this section by recalling results of Bestvina and Mess, Bowditch, and
Swarup, which characterise the hyperbolic groups with locally (path) connected
boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
condition that a hyperbolic group might satisfy.

\begin{definition}
  Double dagger condition
\end{definition}

This property is linked to the connectedness of $\boundary G$ by the following
propositions:

\begin{proposition}
  $\ddag$ implies locally path connected.
\end{proposition}

\begin{proposition}
  no cut point implies $\ddag$.
\end{proposition}

Taken together with the following theorem of Bowditch~\cite{bowditch98b} and
Swarup~\cite{swarup96}, these propositions show that $\boundary G$ is locally
path connected if and only if it is connected.

\begin{theorem}
  If $\boundary G$ is connected then $\boundary G$ does not contain a cut
  point.
\end{theorem}

\subsection{An equivalent condition}

In this section we reinterpret the double dagger condition as a condition
describing the existence of paths in the spheres $K_n$ of
Section~\ref{sec:spheres}. This interpretation gives a more systematic method
for constructing paths in $\boundary G$ from paths in the spheres $K_n$, and
permits a generalisation to higher dimensional connectivity.

\begin{definition}
  New double dagger condition. \todo{State condition.}
\end{definition}

\todo{Prove things about this condition}

\section{Local simple connectedness}

In this section we introduce a new condition that a hyperbolic group might satisfy.

\begin{definition}
  \todo{New condition}
\end{definition}

\todo{If this condition is satisfied then the bounadry is locally simply
connected.}

\section{Simply connected point complements}

In this section we give a sufficient condition for our condition
\todo{condition} to be satisfied.
